Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-02-19 doc/main_jfm.tex
RJR uploaded Biros JFM paper

\title{Behavior of a Two-Dimensional Vesicle Under a Shear Flow via Integral Equation Method}

%\author{Alan N. Jones\aff{1}
%  \corresp{\email{JFMEditorial@cambridge.org}},
%  H.-C. Smith\aff{1}
% \and J.Q. Long\aff{2}}
%
%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}

\author{Rolf Ryham\aff{1},
Bryan Quaife\aff{2},
Szu-Pei Fu\aff{1}
\and Yuan-Nan Young\aff{3}
}
 \affiliation{
\aff{1} Department of Mathematics, \\Fordham University, Bronx, New York 10458, USA
\aff{2}Department of Scientific Computing, \\Florida State University, Tallahassee, Florida 32306, USA
\aff{3}Department of Mathematical Sciences, New Jersey Institute of Technology,\\ Newark, New Jersey 07102, USA
 }

>>>>

%\title{Two-Dimensional Vesicles Under External Flow via Integral Equation Method}
\title{Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations}
%\author{Alan N. Jones\aff{1}
%  \corresp{\email{JFMEditorial@cambridge.org}},
%  H.-C. Smith\aff{1}
% \and J.Q. Long\aff{2}}
%
%\affiliation{\aff{1}STM Journals, Cambridge University Press, The Printing House, Shaftesbury Road, Cambridge CB2 8BS, UK
%\aff{2}DAMTP, Centre for Mathematical Sciences, Wilberforce Road, Cambridge CB3 0WA, UK}

\author{
Szu-Pei Fu\aff{1},
Bryan Quaife\aff{2},
Rolf Ryham\aff{1}, \and
Yuan-Nan Young\aff{3}
}
 \affiliation{
\aff{1} Department of Mathematics, \\Fordham University, Bronx, New York 10458, USA
\aff{2}Department of Scientific Computing, \\Florida State University, Tallahassee, Florida 32306, USA
\aff{3}Department of Mathematical Sciences, New Jersey Institute of Technology,\\ Newark, New Jersey 07102, USA
 }
